---
title: "Major Leagues - Caio Vigo Pereira"
output:
  pdf_document: default
  html_document:
    df_print: paged
    keep_md: yes
---

#Loading the data

I choose to analyze the soccer datasets.

```{r}
my_path<-"C:/Users/Caio Laptop/OneDrive - The University of Kansas/Documents/PhD/11. Courses/19. EECS 731 - Introduction to Data Science/Homework/Section 6 - HW"
setwd(my_path)

spi_matches<-read.csv(paste(my_path,"/Datasets/spi_matches.csv", sep=""),header=T)
spi_global_rankings_intl<-read.csv(paste(my_path,"/Datasets/spi_global_rankings_intl.csv", sep=""),header=T)
spi_global_rankings<-read.csv(paste(my_path,"/Datasets/spi_global_rankings.csv", sep=""),header=T)
```

##Information from the source

SPI Ratings
This file contains links to the data behind our Club Soccer Predictions and Global Club Soccer Rankings.
spi_matches.csv contains match-by-match SPI ratings and forecasts back to 2016.
spi_global_rankings.csv contains current SPI ratings and rankings for men's club teams.
spi_global_rankings_intl.csv contains current SPI ratings and rankings for men's international teams.


#Analyzing my 3 datasets

```{r}
names(spi_matches)
head(spi_matches)
dim(spi_matches)
typeof(spi_matches)
str(spi_matches)
```

```{r}
names(spi_global_rankings_intl)
head(spi_global_rankings_intl)
dim(spi_global_rankings_intl)
typeof(spi_global_rankings_intl)
str(spi_global_rankings_intl)
```


```{r}
names(spi_global_rankings)
head(spi_global_rankings)
dim(spi_global_rankings)
typeof(spi_global_rankings)
str(spi_global_rankings)
```

##Loading some packages

```{r}
library(stargazer)
library(Amelia) # for missmap() function
```

#Taking a look on the Descriptive Statistics

```{r}
stargazer(spi_matches, type='text', align=TRUE, digits=2)
```

```{r}
stargazer(spi_global_rankings, type='text', align=TRUE, digits=2)
```

```{r}
stargazer(spi_global_rankings_intl, type='text', align=TRUE, digits=2)
```

#Checking for any NA's in the dataframe.

```{r}
missmap(spi_matches,col=c('yellow','black'),y.at=1,y.labels='',legend=TRUE)
```

```{r}
missmap(spi_global_rankings,col=c('yellow','black'),y.at=1,y.labels='',legend=TRUE)
```


```{r}
missmap(spi_global_rankings_intl,col=c('yellow','black'),y.at=1,y.labels='',legend=TRUE)
```


## Replacing missing values with the mean
```{r}
spi_matches<-spi_matches[,6:22]
for(i in 1:ncol(spi_matches)){
  spi_matches[is.na(spi_matches[,i]), i] <- mean(spi_matches[,i], na.rm = TRUE)
}
```

## Checking if there is any missing value after the changes
```{r}
missmap(spi_matches,col=c('yellow','black'),y.at=1,y.labels='',legend=TRUE)
```

```{r}
#set a seed 
set.seed(999)

library(caTools)
#Split the data , `split()` assigns a booleans to a new column based on the SplitRatio specified. 

split <- sample.split(spi_matches,SplitRatio =0.75)


train <- subset(spi_matches,split==TRUE)
test <- subset(spi_matches,split==FALSE)
```

```{r}
team_1_model <- lm(score1 ~ proj_score1 + importance1 + xg1 + nsxg1 + spi1 + prob1, data=train)
team_2_model <- lm(score2 ~ proj_score2 + importance2 + xg2 + nsxg2 + spi2 + prob2, data=train)
# summary(team_1_model)
# summary(team_2_model)
stargazer(team_1_model, type='text', align=TRUE, digits=2)
stargazer(team_2_model, type='text', align=TRUE, digits=2)
```

```{r}
# test$predicted.medv <- predict(team_1_model,test)
# test<- na.omit(test$predicted.medv)
```

#Predictions plots

```{r}
predict_team_1_model <- predict(team_1_model,test)
predict_team_2_model <- na.omit(predict(team_2_model,test))

plot(test$score1,predict(team_1_model,test))
plot(test$score2,predict(team_2_model,test))
```

```{r}
error <- test$score1-predict_team_1_model
rmse <- sqrt(mean(error)^2)
rmse
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
