---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

Loading the data.
I choose to analyze the soccer datasets.

```{r}
my_path<-"C:/Users/Caio Laptop/OneDrive - The University of Kansas/Documents/PhD/11. Courses/19. EECS 731 - Introduction to Data Science/Homework/Section 6 - HW"
setwd(my_path)

spi_matches<-read.csv(paste(my_path,"/Datasets/spi_matches.csv", sep=""),header=T)
spi_global_rankings_intl<-read.csv(paste(my_path,"/Datasets/spi_global_rankings_intl.csv", sep=""),header=T)
spi_global_rankings<-read.csv(paste(my_path,"/Datasets/spi_global_rankings.csv", sep=""),header=T)
```

Information from the source:
SPI Ratings
This file contains links to the data behind our Club Soccer Predictions and Global Club Soccer Rankings.
spi_matches.csv contains match-by-match SPI ratings and forecasts back to 2016.
spi_global_rankings.csv contains current SPI ratings and rankings for men's club teams.
spi_global_rankings_intl.csv contains current SPI ratings and rankings for men's international teams.


Now I will analyze my 3 datasets.

```{r}
names(spi_matches)
head(spi_matches)
dim(spi_matches)
typeof(spi_matches)
str(spi_matches)
```

```{r}
names(spi_global_rankings_intl)
head(spi_global_rankings_intl)
dim(spi_global_rankings_intl)
typeof(spi_global_rankings_intl)
str(spi_global_rankings_intl)
```

```{r}

```


```{r}
library(stargazer) #to report regression results in Latex format
stargazer(wage1, type='text', align=TRUE, digits=2)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
